---
title: "httr_requests"
output: html_notebook
---

# HTTR Requests

HTTR requests as conversations. Ask for something `GET`; send something `POST`.

## GET

```{r}
# Load the httr package
library(httr)

# Make a GET request to http://httpbin.org/get
get_result <- GET("http://httpbin.org/get")

result <- content(get_result)
print(get_result)
str(result)
```

Every `GET` or `POST` gets a Status. Rule of thumb: if it starts with 2 or 3, good; if it starts with 4, then there's a problem.  

## POST

```{r}
# Make a POST request to http://httpbin.org/post with the body "this is a test"
post_result <- POST(url = "http://httpbin.org/post", body = "this is a test")

# Print it to inspect it
post_result
```

### Error handling

```{r}
fake_url <- "http://google.com/fakepagethatdoesnotexist"

# Make the GET request
request_result <- GET(fake_url)

# Check request_result
if(http_error(request_result)){
	warning("The request failed")
} else {
	content(request_result)
}
```


### Query Construction

The actual API query (which tells the API what you want to do) tends to be in one of the two forms. The first is directory-based, where values are separated by / marks within the URL. The second is parameter-based, where all the values exist at the end of the URL and take the form of key=value.

```{r}
# Construct a directory-based API URL to `http://swapi.co/api`,
# looking for person `1` in `people`
directory_url <- paste("http://swapi.co/api", "people", "1", sep = "/")

# Make a GET call with it
result <- GET(directory_url)
```

For parameters, instead of using `paste` use a named list and `GET`.

```{r}
# Create list with nationality and country elements
query_params <- list(nationality = "americans", 
    country = "antigua")
    
# Make parameter-based call to httpbin, with query_params
parameter_response <- GET("https://httpbin.org/get", query = query_params)

# Print parameter_response
parameter_response
```

### Do not over GET 

```{r}
# Construct a vector of 2 URLs
urls <- c("http://fakeurl.com/api/1.0/", "http://fakeurl.com/api/2.0/")

for(url in urls){
    # Send a GET request to url
    result <- GET(url)
    # Delay for 5 seconds between requests
    Sys.sleep(5)
}
```

### All together

```{r}
get_pageviews <- function(article_title){
  url <- paste(
    "https://wikimedia.org/api/rest_v1/metrics/pageviews/per-article/en.wikipedia/all-access/all-agents", 
    article_title, 
    "daily/2015100100/2015103100", 
    sep = "/"
  )   
  response <- GET(url, user_agent("my@email.com this is a test")) 
  # Is there an HTTP error?
  if(http_error(response)){ 
    # Throw an R error
    stop("the request failed") 
  }
  # Return the response's content
  content(response)
}
```

