---
title: "JSON & XML"
output: html_notebook
---

Let's work with the most common formats that an API will give you back: JSON & XML.

# JSON

JavaScript Object Notation (JSON). Great for hierarchical data. Either objects (`{}`) or arrays (`[]`).

```{r}
# Get revision history for "Hadley Wickham"
resp_json <- rev_history("Hadley Wickham")

# Check http_type() of resp_json
http_type(resp_json)

# Examine returned text with content()
content(resp_json, as = "text")

# Parse response with content()
content(resp_json, as = "parsed")

# Parse returned text with fromJSON()
library(jsonlite)
fromJSON(content(resp_json, as = "text"))
```

## Using rlist

```{r}
# Load rlist
library(rlist)

# Examine output of this code
str(content(resp_json), max.level = 4)

# Store revision list
revs <- content(resp_json)$query$pages$`41916270`$revisions

# Extract the user element
user_time <- list.select(revs, user, timestamp)

# Print user_time
user_time

# Stack to turn into a data frame
list.stack(user_time)
```

## Using tidyverse

```{r}
library(dplyr)

# Pull out revision list
revs <- content(resp_json)$query$pages$`41916270`$revisions

# Extract user and timestamp
revs %>%
  bind_rows() %>%           
  select(user, timestamp)
```

# XML

```{r}
# Load xml2
library(xml2)

# Get XML revision history
resp_xml <- rev_history("Hadley Wickham", format = "xml")

# Check response is XML 
http_type(resp_xml)

# Examine returned text with content()
rev_text <- content(resp_xml, as = "text")
rev_text

# Turn rev_text into an XML document
rev_xml <- read_xml(rev_text)

# Examine the structure of rev_xml
xml_structure(rev_xml)
```

## XPATHS

XPATHs are designed to specifying nodes in an XML document. Remember /node_name specifies nodes at the current level that have the tag node_name, where as //node_name specifies nodes at any level below the current level that have the tag node_name.

```{r}
# Find all nodes using XPATH "/api/query/pages/page/revisions/rev"
xml_find_all(rev_xml, "/api/query/pages/page/revisions/rev")

# Find all rev nodes anywhere in document
rev_nodes <- xml_find_all(rev_xml, "//rev")

# Use xml_text() to get text from rev_nodes
xml_text(rev_nodes)
```

Attributes (next to the tags):

```{r}
# All rev nodes
rev_nodes <- xml_find_all(rev_xml, "//rev")

# The first rev node
first_rev_node <- xml_find_first(rev_xml, "//rev")

# Find all attributes with xml_attrs()
xml_attrs(first_rev_node)

# Find user attribute with xml_attr()
xml_attr(first_rev_node, "user")

# Find user attribute for all rev nodes
xml_attr(rev_nodes, "user")
```

`xml_attrs()` takes a nodeset and returns all of the attributes for every node in the nodeset. `xml_attr()` takes a nodeset and an additional argument attr to extract a single named argument from each node in the nodeset.

```{r}
get_revision_history <- function(article_title){
  # Get raw revision response
  rev_resp <- rev_history(article_title, format = "xml")
  
  # Turn the content() of rev_resp into XML
  rev_xml <- read_xml(content(rev_resp, "text"))
  
  # Find revision nodes
  rev_nodes <- xml_find_all(rev_xml, "//rev")

  # Parse out usernames
  user <- xml_attr(rev_nodes, "user")
  
  # Parse out timestamps
  timestamp <- readr::parse_datetime(xml_attr(rev_nodes, "timestamp"))
  
  # Parse out content
  content <- xml_text(rev_nodes)
  
  # Return data frame 
  data.frame(user = user,
    timestamp = timestamp,
    content = substr(content, 1, 40))
}

# Call function for "Hadley Wickham"
get_revision_history("Hadley Wickham")
```

